\subsection{Server Test plan}
The server
will be tested in the form of unit tests. These will run tests that check a specific piece of functionality of each subsystem. To ensure that all systems operate together integration testing will be performed. To ensure proper performance acceptance testing will also be ran.
\subsubsection{Unit testing}
Unit testing is performed per function used one or a series of functional testing and interaction tests. Functional testing concerns the behaviour of systems tested on based on input and output. Interaction testing concerns behaviour of multiple systems based on their interactions in the form of function call patterns. Because the server is written using Java, we will use the Java testing frameworks JUnit\footnote{Testing framework used to automate testing in Java. Home page of JUnit: \url{www.junit.org/}} for functional testing, and for interaction testing we will use Mockito \footnote{Testing framework for JUnit, used to mock classes and let them performed predefined interactions, and test on interactions made between objects. Home page of Mockito for JUnit: \url{code.google.com/p/mockito/}}.

\paragraph{Filesystem read testing:}

\begin{enumerate}
\item Issue a getFile() call on a .syn file that contains the a relatively simple circuit  and a list with enough proteins, which are all assigned to edges.

\item Issue a getFile() call on a .syn file that contains the a relatively simple circuit  and a list with not enough proteins, where undefined proteins are assigned to edges. Validate that an exception is thrown.\item Issue a getFile() call on  a .syn file that contains the  circuit of item 1, with two simulation data series.
\item Issue a getFile() call on  a corrupt .syn file that contains the above circuit, but with corruptions in each part.
Validate that the reader will detect this and throw an exception.
\item Issue a getFile() call on  a .syn file that contains the an extremely large circuit. Validate that the function call ends within a certain time. 
\item Issue a listFiles() call and validate that all .syn files in the specified folder are returned.

\item Issue a listProteins() call when a valid document listing the TF's and CDS's is present and validate that all the listed elements are read.
 Boundary test by varying the number of elements from 0 to 3, and also one with in the order of 1000 elements.\item Issue a listProteins() call when an  invalid document listing TF's and CDS's is present and validate that an exception is thrown.
\item Issue a listProteins() call when no document listing TF's and CDS's is present and validate that an exception is thrown.\end{enumerate}

\paragraph{Filesystem write testing:}

\begin{enumerate}
\item Issue a putFile() call with a .syn filename, and a relatively simple circuit JSON.
\item  Issue a putFile() call with a .syn filename, and a  relatively simple circuit JSON, with two simulation data series.
\item  Issue a putFile() call with a .syn filename and corrupt circuit JSON. Validate that an exception is thrown. 
\end{enumerate}

\paragraph{HTTP API:
}\begin{enumerate}
\item Issue a listFiles() call and validate that interactions with the filesystem subsystem have been made. Mock the filesystem and to make it return a certain set of files, and validate that the correct JSON is generated.
\item Issue a getFile(filename) call with an existent filename and validate that the correct call is made to the filesystem reader to read the given filename.
\item Issue a getFile(filename) call with an non-existent filename and validate that the filesystem reader throws an exception.
\item Issue a getFile(filename) call with an existent filename of a corrupt file, and validate that the filesystem reader throws and exception.
\item Issue a putFile(circuit, filename) call with a provided circuit and filename, and validate  that the correct call to the filesystem has been made. Mock the filesystem to make it return true and false with all possible exceptions for separate test. Validate that the correct JSON is generated.\item Issue a listProteins() call. Mock the filesystem reader to provide predefined sets of return values, and validate that the correct JSON is generated. Boundary test by varying the set of return values from 0 to 3, and one with in the order of 1000. \item Issue a circuitToSBML() call with a relatively simple circuit containing nodes, edges, assigned proteins, and a simulation data series. Ensure the correct call is made to the filesystem writer. Also ensure that the returned XML is a valid SBML schema.\item Issue several validate(circuit) calls and ensure that the correct call has been made to the validation subsystem. Mock the validation subsystem to return true and false with all possible exceptions and ensure that the right JSON is generated.
\item Mock the validation subsystem as described in test 8 and mock the simulation subsystem. Issue a simulate(circuit, inputValues) call and ensure that validate() is called first (it returning false in this test) and validate that the simulation subsystem is not called. Function arguments can be arbitrary. 
\item Mock the validation subsystem as described in test 8 and mock the simulation subsystem. Issue a simulate(circuit, inputValues) call with a valid circuit and arbitrary input values and ensure that validate() is called first (it returning true in this test). Validate that the simulation subsystem is then called and returns the output values. Mock the simulator to return output values data series of length 0 to 3. Validate that the correct JSON is generated.\end{enumerate}
\paragraph{JSBML Solver testing/simulator testing:}
\begin{enumerate}
\item 
Call the simulator  to solve a relatively simple circuit and ensure that a new separate solver thread is started and output values are returned within a certain time.
\item Issue a simulate() call with  to solve a extremely large circuit and ensure that a new solver thread is started. If the solver crashes or hangs for longer than a specified time, ensure that an exception is thrown and the thread is terminated.
\end{enumerate}

\paragraph{Validator testing:}

\begin{enumerate}
\item Issue a validate() call with a valid circuit and ensure that true is returned.
\item Issue a validate() call with a set of invalid circuits, in which there is a invalid circuit for each type of exception that can be thrown by the validator. Ensure that for each circuit the correct exception is thrown. 
\end{enumerate}
\textbf{Webserver testing}
\begin{enumerate}
\item Request a connection with the webserver with the request to send the GUI and validate that a connection is set up and the GUI page is  served. 
\item Ensure that when a previous connection to a client is still open, and the client makes a new HTTP request, the same connection is used. 
\item Ensure that after a client HTTP request is server and a connection is idle for a certain time, it is discarded.\end{enumerate}
\textbf{Controller testing}
\begin{enumerate}
\item Mock the simulator to make take forever to complete a function call. Ensure that after a certain time, the  simulator thread is terminated. Ensure that an exception is thrown to the client.

\item Mock the validator to make take forever to complete a function call. Ensure that after a certain time, the  validator thread is terminated. Ensure that an exception is thrown to the client.

\item Mock the webserver to make take forever to complete a function call. Ensure that after a certain time, the  webserver thread is terminated and restarted. Ensure that an exception is thrown to the client.
\end{enumerate}

\subsubsection{Integration testing}
Testing of the integration with the client will be done by testing the HTTP API, and testing of the integration of the the server subsystems will be covered by the following unit tests that mock the client by creating a connection with the webserver and sending HTTP API calls in the form of JSON.

\begin{enumerate}
\item Issue a putFile(circuit) call with a relatively simple model and then a getFile(circuit) call on the just saved circuit and validate that the same circuit is returned.
\item Issue a simulate() call with a relatively simple model and arbitrary input values and ensure that a output values data series is returned. Then issue a putFile(circuit) call with the current circuit, and then a getFile(circuit) call on the previously saved circuit. Ensure that the same circuit is loaded with the simulation data series.
\item Issue two putFile(cricuit) calls at almost the same  time, but with different models and the same filename. Ensure that the filesystem writer handled the requests consecutively and only the last circuit
persists on the filesystem.\end{enumerate}

\subsubsection{Acceptance testing}
User stories developed for each development run provide valuable information about how much the server side weighs in the result. For each user story we'll create one or more acceptance tests, and for those that also include server calls, most can be valued by the responsiveness and stability of the server. For some tests this is already defined as a certain time within which the server has to finish the job. What these times should be will be decided during acceptance testing based on feedback from the user on the responsiveness of the application.
