%&latex
\documentclass[a4paper]{article}

\usepackage[dutch]{babel}
\usepackage{tabularx}
\usepackage{fullpage}
\usepackage{booktabs}

\newcounter{step}
\setcounter{step}{1}
\newcommand{\step}{\arabic{step}\stepcounter{step}}

% something from above messes up pdf output, so force it.
\pdfoutput=1

\begin{document}

%+Title
\title{Acceptance testing results}
\author{Christ Akkermans}
\date{\today}
\maketitle
%-Title



\section{Acceptance testing results}
This acceptance test was run by a aerospace engineering student. It was tested on FireFox 12.0 with an core-i7. 
These are his findings.

\subsection{Basic startup and workspace initialization}
Appears not to connect to stub server at all. Did not check HTTP activity.

Visual artifact when dragging input block.

Raw error as reported by Firebug:
Circuit details element (top right) entered an invalid state. Should be either the editing [sic] or displaying. Is checked by comparing the button inner HTML.
http://zelula.us.to/scrum5/program/js/gui-workspace.js
Line 739


\subsection{File opening}
No comment.

\subsection{File saving}
Warning is briefly shown, but file is saved anyway on first click.

\subsection{Create simple circuit}
Works fine.

\subsection{Create and simulate a 2-to-1 multiplexer:}
Multiplexer is not available or shown in UI? There is no preset option for this test.

\subsection{Compound Gates}
No further remarks.

\subsection{General bugs}
Nothing to mention.

\vfill
\subsection{Usability grading}
Here the tester can give grades for specific and overall aspects of the usability of the application. Of course written remarks and feedback on certain aspects are also very valuable, and we encourage the tester to make these along with providing grades. On some aspects an explanation is provided in the footnotes.

In the following table, the grades correspond to the following valuations;\\ 1 = very bad, 3 = bad, 5 = moderate/average, 7 = good, 9 = very good.
\begin{center}
\begin{tabularx}{\textwidth}{p{10cm} cc cc c cc cc} \toprule
\textbf{Aspect} & \multicolumn{1}{c}{\textbf{Score on aspect}} \\ \midrule
Usability of circuit modelling &6\\ \midrule
Usability of circuit management \footnote{The ease of use and learability of importing, exporting, saving, opening, browsing and editing of circuit details.} &9 \\ \midrule
Responsiveness &7 \\ \midrule
Performance &7 \\ \midrule
Affordance \footnote{The degree in which the UI intuitively implies it's functionality and use.} &8 \\ \midrule
Presentation of data \footnote{The quality of communication of, for example; simulation output data, validation results, input data, protein listings} &8 \\ \midrule
Visual appeal &7 \\ \midrule
\textbf{Overal application usability} &\textbf{7} \\ \bottomrule
\end{tabularx}
\end{center}

\end{document}


