\subsection{Interface} % (Jan Pieter)

% include common command to define the windows.
\input{pictures/interface-common}

When starting the program for the first time, the user is presented with window in build mode (\ref{fig-interface-empty}) containing a sidebar with the three elemental building blocks: wire, an AND-gate and a NOT-gate. The lower part of the sidebar is reserved for user-defined \textit{substructures}, as mentioned in functional requirement 1.
The remainder of the window is a working area which is initially empty.
On the top bar two menu items are present. One for basic file actions like export, save and import, the second for actions concerning the simulation of the brick.

\begin{figure}[h!]
	\label{fig-interface-empty}
	\caption{Initial program state.}
	\centering\begin{tikzpicture}
		\programGUI{untitled.sbml}

		\sidebar
	\end{tikzpicture}
\end{figure}

\noindent To model a circuit, the elemental parts can be dragged into the working area, the gates may be connected using wires. The interface state after adding some wires is proposed in figure \ref{fig-interface-building}.

\begin{figure}[h!]
	\label{fig-interface-building}
	\caption{After adding some gates to the working area.}
	\centering
	\begin{tikzpicture}
		\programGUI{example42.sbml}
		\sidebar

		%define some gates in working area
		\draw ( -2.5, 2.5) \gateAND -- ++(1, 0) \gateNOT -- ++(1, 0) -- ++(0, -1) \gateAND \terminal;

		\draw ( -2.5, .9)  \gateAND -- ++( 4,0);
		
	\end{tikzpicture}
\end{figure}

\pagebreak
\noindent After building the circuit, the user has to select which protein to use for each signal. This can be done during the building process aswell. In figure \ref{fig-interface-selectProtein} the protein selection dialog is shown for one signal, for some other signals the representing protein is shown above.
\begin{figure}[h!]
	\label{fig-interface-selectProtein}
	\caption{Selecting a protein for the signal.}
	\centering
	\begin{tikzpicture}
		\programGUI{example42.sbml}
		\sidebar

		\draw ( -2.5, 2.5) node[above right] {A} \gateAND -- node [above] {C} ++(1, 0) \gateNOT -- node [above] {F} ++(1, 0) -- ++(0, -1) \gateAND node[above left] {G} \terminal ;
	
		\draw ( -2.5, .9)  \gateAND -- ++( 4,0);

		\draw ( 0, 1) [fill=black!30,line width=1pt] rectangle ++(3, -3)
			++(-3, 3) node [anchor=north west] {\textit{Select signal}} rectangle ++(3, -.6)
			++(-3, 0) node [anchor=north west] {protein A} rectangle ++(3, -.6)
			++(-3, 0) node [anchor=north west] {protein B} rectangle ++(3, -.6)
			++(-3, 0) node [anchor=north west] {protein C} rectangle ++(3, -.6)
			++(-3, 0) node [anchor=north west] {protein D} rectangle ++(3, -.6);
	\end{tikzpicture}
\end{figure}