%
\documentclass[a4paper]{article}

\input{../scrumplan-common}

\title{Project Zelula - SCRUM plan \#4}

\author{Group 5/E:\\
Felix Akkermans \\
Niels Doekemeijer \\
Thomas van Helden \\
Albert ten Napel \\
Jan Pieter Waagmeester}

\begin{document}

\maketitle

%~ • The selection of a set of features (important features first).
%~ • A List of the tasks for each feature.
%~ • The assignment of students to tasks.
%~ • An estimation of the effort per task.
%~ • The actual effort per task (after the iteration is done).
%~ • Short reflection on the main problems and adjustments of the iteration planning
\section{Introduction}
In this SCRUM plan we define the tasks we want to complete in this sprint. Every task is assigned to one or two developers and an estimate is provided for the effort required.

For each SCRUM run a milestone is created at GitHub, with issues for the tasks selected. The issues for this milestone can be found on: \githubmilestone{11}.

\section{Selection and assignment of tasks}
This is the fourth sprint of our project. During this sprint we will finish the server-side simulating, start with the output visualisation and start with the final report.

\paragraph{Available time}
The time available is five  mornings in two weeks by five people. That's about twenty hours per person. Including meetings we come to an estimate of 90 hours of actual working. 

A list of tasks, assignments and effort estimations is included in the table on the next page.

\begin{center}
\begin{tabularx}{\textwidth}{r p{8cm} | l | cc}
\tasktableheading

\task{73}
	{Client: Resize}
	{Felix}
	{6}{-}

\task{45}
	{Client: Finish Save Circuit}
	{Felix}
	{1}{5}

\task{66}
	{Client: Acceptance testing}
	{Felix}
	{8}{4}

\task{72}
	{Client: Extend input definition}
	{Jan Pieter}
	{6}{6}

\task{54}
	{Client: Simulate Circuit}
	{Jan Pieter}
	{2}{2}

\task{53}
	{Client: Output visualization}
	{Niels}
	{2}{6}

\task{68}
	{Client: Refactor JavaScript}
	{Niels}
	{6}{6}

\task{67}
	{Test Coverage}
	{Albert + Thomas}
	{9}{4+4}

\task{69}
	{Finish Scrum plan 4}
	{Albert}
	{2}{2}

\task{70}
	{Scrum plan 5 scaffolding}
	{Albert}
	{2}{1}

\task{42}
	{Leftover Thomas}
	{Thomas + Felix}
	{5}{9+8}

\task{52}
	{Final report: Key Problems/Solutions}
	{Thomas}
	{4}{1}

\task{55}
	{Final report: Reflection Teamwork}
	{Everyone}
	{5*1}{-}

\task{}
	{Code Review}
	{Everyone}
	{5*3}{14} % Jan Pieter: 3, Niels: 3, Albert: 2, Felix: 3, Thomas: 3

\subtotal{73}{72}
 
\subheading{
	Optional tasks
}

\task{71}
	{Client: Compound Gates}
	{}
	{12}{-}

\task{65}
	{Client: Save input/output gate positions}
	{}
	{-}{-}

\task{43}
	{Client: Polish circuit styles}
	{}
	{-}{-}

\task{43}
	{Client: Style of gate while dragging}
	{}
	{-}{-}

\task{43}
	{Client: Size and drop area of endpoints}
	{}
	{-}{-}

\task{43}
	{Client: Deleting of wires and gates using delete}
	{}
	{-}{-}

\task{}
	{Client: Highlighting/selecting gates to move multiple or delete multiple}
	{}
	{-}{-}

\task{}
	{Client: Input and output fields resize and display open connections}
	{}
	{-}{-}


\subtotal{-}{-}

\subheading{Added tasks}

\task{61}
	{Extended input signal modification: toggle ranges}
	{Jan Pieter}
	{-}{5}

\task{}
	{Created \verb|new| menu item}
	{Jan Pieter}
	{-}{1}

\task{74}
	{Edit circuit (file)name and description}
	{Felix}
	{-}{4}

\subtotal{-}{10}

\grandtotal{73}{82}
\end{tabularx}
\end{center}
\pagebreak
\section{Reflection on this iteration}
In this section we will give a quick review on this iteration. \\

\subsection*{Planning}
We planned to work on the client side simulating and starting with the simulation results. Furthermore we wanted to fix different small gui issues and refactor the Javascript so it would be easier to work with. We also wanted to get more work done on the final report, since there was still a lot to be done in the report.

\subsection*{Implementation}
During this iteration one of the problems we encountered were inadequately communicated commits. This resulted in two persons working on the same thing and committing the work simultaneously. It took some time to figure out what went wrong and how to fix it. \\
Another problem we encountered was that as soon as the output visualisation was in a usable state, we discovered that the simulation results weren't completely correct. The problem still hasn't been found and we have to spent time in the next iteration to find a solution.\\

\end{document}
